### 2013-11-25 patchy-selection-paper.tex
.

In one dimension, we are done (see section~\ref{apx:elliptic_integrals});
in higher dimensions, we are more interested in the mean frequency at a given distance $r$ from a patch.
If we take a radially symmetric patch centered at the origin (so $\gamma$ only depends on $r$), 
and let $\xi(t,r)$ denote the mean occupation frequency at distance $r$,
then the polar form of the Laplacian in $d$ dimensions gives us that \eqref{eqn:derived_fkpp} is
\begin{align}
  \label{eqn:radial_fkpp}
  \partial_t \xi(t,r) = \mu \left( \frac{\sigma^2}{2} \partial_{r}^2 \xi(t,r) + \sigma^2\frac{d-1}{2r} \partial_r \xi(t,r) + \gamma(r) \xi(t,r) (1-\xi(t,r)) \right) .
\end{align}
However, the second term goes to zero as $r \to \infty$,
leading to the same asymptotic behavior for the tail \plr{CITE SOMETHING}.

@@

>>>>

We are interested in the equilibrium frequency,
i.e.\ the mean frequency of the selected allele at migration-selection equilibrium.
The frequency $\phi(x)$ at location $x$ solves
\begin{align}
  \label{eqn:general_phi}
  \frac{\sigma^2}{2} \sum_{k=1}^d \partial_{x_k}^2 \phi(x) + \gamma(x) \phi(x) (1-\phi(x)) = 0 
\end{align}

@@

%%%%%%%%%%
\section{Asymptotics for the equilibrium frequency}
\label{ss:asymptotic_freq}

We provide the above discussion on exact solutions mostly for completeness;
in practice, we use asymptotics of the solutions.
These are furthermore available for $d=2$, where we have no analytic solutions.
In $d=2$ (and higher) dimensions, we are more interested in the mean frequency at a given distance $r$ from a patch.
Suppose therefore that the patch is radially symmetric,
and that the allele is uniformly deleterious outside of some radius $r_0$
(in the notation above, $\gamma(x) = -s_m$ for $|x|>r_0$).
Then, denoting by $\phi(r)$ the mean occupation frequency at distance $r$ at equilibrium,
the polar form of the Laplacian in $d$ dimensions translates equation \eqref{eqn:general_phi} to
\begin{align}
  \label{eqn:radial_phi}
  \frac{\sigma^2}{2} \partial_{r}^2 \phi(r) + \sigma^2\frac{d-1}{2r} \partial_r \phi(r) &= s_m \phi(r) (1-\phi(r)) \quad r>r_0 , \\
  \phi(r_0) = \phi_0 , \qquad \phi(r) \ge 0 .
\end{align}
We wish to find the asymptotic behavior of $\phi$ for large $r$.
The argument can likely be extended to patches that are not radially symmetric.

The solution with $d=2$ is $C Y_0(ir) \sim C e^{r}/\sqrt{2 \pi r}$ (G\&R 8.451.2).
